User Preferences in Graphical and Textual Interfaces for Kubernetes

### 2021-08-24 Draft.tex
refined study setup

During the study sessions, participants completed a Kubernetes task using the kubectl CLI and the OpenShift console. Half of the participants used the kubectl CLI first and the other half used the OpenShift console first. We employed a classic ``Think Aloud'' user evaluation method. Video and audio from the sessions were recorded using Webex for later transcription and analysis.

@@

Participants were given a GitHub repo with the application files and task instructions. No time limit was set to complete the task. If participants got stuck while completing the task, hints specific to each tool interface were provided in hyperlinks below the task instructions. Participants were told to think aloud while completing the task and given a prompt to continue if they fell silent for more than 15 seconds. The goal of the Kubernetes task was to create an application in a namespace, find the deployment pods that have the string ``magic key'' in their logs, delete the application, and then delete the namespace.

>>>>

During the study sessions, participants completed a Kubernetes task using the kubectl CLI and the OpenShift console. The goal of the Kubernetes task was to create an application in a namespace, find the deployment pods that have the string ``magic key'' in their logs, delete the application, and then delete the namespace. Participants were given a GitHub repo with the application files and task instructions. No time limit was set to complete the task. If participants got stuck while completing the task, hints specific to each tool interface were provided in hyperlinks below the task instructions. Half of the participants used the kubectl CLI first and the other half used the OpenShift console first. We employed a classic ``Think Aloud'' user evaluation method in which participants were asked to think aloud while completing the task and given a prompt to continue if they fell silent for more than 15 seconds. Video and audio from the sessions were recorded using Webex for later transcription and analysis.

@@
